ensembles

### 2016-05-13 CORDEX/ensembles.Rmd
Added a set with new Rmd scripts

```{r}
fit.atm <- lm(dT ~ atm.grid + atm.lev + atm.top + oce.lev + oce.z,data=X)
print(summary(fit.atm))
```

>>>>

```{r}
fit.atm <- lm(dT ~ atm.grid + atm.lev + atm.top + oce.lev + oce.z +
                   atm.grid*atm.lev + atm.grid*atm.top +       # interactions
                   atm.grid*oce.lev + atm.grid*oce.z,data=X)
print(summary(fit.atm))
```
